maxent model avec xvalidation (year-based test training)

### 2019-05-16 src/maxent_avec_xvalidation.Rmd
plot generation for report

```{r pre-install & load packages, include=FALSE}
options(java.parameters = "-Xmx2g" )#needs to run before dismo loaded - boosts memory for java to 1g
packages <- c("dismo", "stringr", "rJava", "raster", "ecospat", "bossMaps", "lattice", "tidyr", "enmSdm", "ggplot2", "plyr")
source("../src/ipak.R")
ipak(packages)
```

@@

write.csv(aicsum, "../output/maxent/models/aicsummary.csv", row.names = FALSE)
```

@@

```{r permulation plot}
permelt <- melt(permu, id = "Month") #need to melt the data into this format for ggplot
perpl <- ggplot(data = permelt, aes(x = Month, y = value, fill = variable)) + geom_bar(stat = "identity") + scale_fill_brewer(palette = "Set1")
png("../output/maxent/models/permutation_plot.png")
print(perpl)
dev.off()
```

@@

#plots by depth

@@

>>>>

```{r pre-install & load packages, include=FALSE}
options(java.parameters = "-Xmx2g" )#needs to run before dismo loaded - boosts memory for java to 1g
packages <- c("dismo", "stringr", "rJava", "raster", "ecospat", "bossMaps", "lattice", "tidyr", "enmSdm", "ggplot2", "plyr", "reshape2")
source("../src/ipak.R")
ipak(packages)
```

@@

mthord <- c("jan", "mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec") # a list of months to order by
aicsum <- aicsum[match(mthord, aicsum$Month), ] #reorder based on mthord
write.csv(aicsum, "../output/maxent/models/aicsummary.csv", row.names = FALSE)

@@

```{r permulation plot}
permelt <- melt(permu, id = "Month") #need to melt the data into this format for ggplot
perpl <- ggplot(data = permelt, aes(x = Month, y = value, fill = variable)) + geom_bar(stat = "identity") + scale_fill_brewer(palette = "Set1")
png("../output/maxent/models/permutation_plot.png")
print(perpl)
dev.off()

#for jan

permuj <- subset(permu, Month == "jan")
permelt <- melt(permuj, id = "Month") #need to melt the data into this format for ggplot
perpl <- ggplot(data = permelt, aes(x = Month, y = value, fill = variable)) + geom_bar(stat = "identity") + scale_fill_brewer(palette = "Set1")
png("../output/maxent/models/permutation_plot_jan.png")
print(perpl)
dev.off()
```

@@

#plots by depth for MPA threshold

@@

# quickly adding some black to some plots for mj slr
```{r}
mthlst <- c("jan", "mar", "apr", "may", "jun", "jul", "aug", "sep", "oct", "nov", "dec")

for(m in 1:length(mthlst)){
  mthna <- mthlst[m]
  replst11 <- list.files(paste0("../output/maxent/predictions/", mthna), pattern =  ".*11.7737.*.asc", full.names = TRUE)
  replst221 <- list.files(paste0("../output/maxent/predictions/", mthna), pattern =  ".*221.141.*.asc", full.names = TRUE)
  replst508 <- list.files(paste0("../output/maxent/predictions/", mthna), pattern =  ".*508.64.*.asc", full.names = TRUE)
  replst <- c(replst11, replst221, replst508)
  for (r in 1:length(replst)){
    ras <- raster(replst[r])
    ascname <- names(ras)
    plot(ras, colNA = 'black', png(paste0("../output/maxent/predictions/", mthna, "/", ascname, ".png")), overwrite = TRUE)
    dev.off()
  }
}

replst163 <- list.files("../output/maxent/predictions/jul/", pattern =  ".*163..*.asc", full.names = TRUE)
for (r in 1:length(replst163)){
    ras <- raster(replst163[r])
    ascname <- names(ras)
    plot(ras, colNA = 'black', png(paste0("../output/maxent/predictions/jul/", ascname, ".png")), overwrite = TRUE)
    dev.off()
}

back <- raster("../output/maxent/predictions/mar/binary_avg_medprob_avg_cloglog_1.55586.asc")
replst163 <- list.files("../output/maxent/predictions/jan/", pattern =  ".*avg_2d.*.asc", full.names = TRUE)
for (r in 1:length(replst163)){
    ras <- raster(replst163[r])
    ascname <- names(ras)
    bkras <- overlay(back, ras, fun=function(x,y){return(x+y)})
    plot(bkras, colNA = 'black', png(paste0("../output/maxent/predictions/jan/", ascname, ".png")), overwrite = TRUE)
    dev.off()
}
